Dissecting Neural Style Transfer

### 2019-05-26 paper/paper.tex
1

\begin{document}
\title{Neural Network Transfer extended with Multiple Style Images}
\author{Xi Du}
\institute{Australian National University, Australia\\
\email{u6559090@anu.edu.au}}
\maketitle 
\begin{abstract}
\cite{method}

@@

\subsection{Preliminary}

>>>>

\begin{document}
\title{Dissecting Neural Style Transfer}
\author{Xi Du}
\institute{Australian National University, Australia\\
\email{u6559090@anu.edu.au}}
\maketitle 
\begin{abstract}
\cite{method}

@@

\subsection{Deep Neural Network}

For the purpose of implementing and even extending neural style transfer algorithms,
it is not necessary to understand how a neural network is trained, because
we can use pretrained model for example vgg19 \cite{vgg19}.

It is necessary to point out that a deep neural network that neural style transfer
is concerend about
is just a sequence of functions
$F_1,F_2,F_3,...$
whose inputs and outputs are all multi-dimensional arrays, as illustrated in Figure \ref{f1f2f3}.
\begin{figure}
\center
\includegraphics[width=0.6\textwidth]{f1f2f3.pdf}
\caption{A deep neural network \label{f1f2f3}}
\end{figure}
Because the arrays have usually more than two numbers of dimensions
they are not really matrices.
The arrays are called tensors (as in TensorFlow or torch.Tensor in PyTorch) 
but actual tensor algebra in a mathematical sense is rarely relevant.
The functions need to be differentiable, which is handled automatically by modern 
deep learning frameworks.
Other than that we can treat the functions as blackboxes because we are 
not concerned of training the model.

For the vgg19 model that most neural style transfer implementations available are based on,
The inputs and outpus of each layer are all arrays with 4 dimensions.
The word ``dimension'' here may mean something slightly different from what ``dimension'' means in
for example ``$3$-dimension vector''. 
Some people call the number of dimensions ``rank'' which would then raise another confusion with the rank of matrices.

The 1st dimension is the ``batch'' dimension, which means that you can put several images through the
series of functions.
In neural style transfer implementations it is usually just one image each time.
So the 1st dimension is always 1, even between the $F$ functions, throughout this work.

The 2nd dimension is the ``feature'' dimension. For a raw RGB image, it is 3.
Intermediate values between, for example, $F_3$ and $F_4$, usually 
have a size much larger than 3, such as 64 or 128

\subsection{Vanilla neural style transfer}
